### 2014-06-06 method.tex
typos

What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.  We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other of the methods described above, it can effectively learn a "Timely" approach to the detection computation.

We first review the base model that our work is derived from, the R-CNN method in the following subsection.  We then present our approach to region prioritization using simple features based on basic region and gradient properties in \autoref{sec:region} and \autoref{sec:gradient}.  We then consider mid-level features in \autoref{sec:dense}, based on a Pyramid scheme which amortizes the computation across overlapping regions, but does not use them for the subsequent computation.  Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time.

>>>>

What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.  We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other methods below, it can effectively learn a "Timely" approach to the detection computation.

We first review the base model that our work is derived from, the R-CNN method, in the following subsection.  We then present our approach to region prioritization using simple features based on basic region and gradient properties in \autoref{sec:region} and \autoref{sec:gradient}.  We then consider mid-level features in \autoref{sec:dense}, based on a Pyramid scheme which amortizes the computation across overlapping regions, but does not use them for the subsequent computation.  Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or expoit more costly mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time.
